### 2018-08-27 mycv/subs/papers.tex
updates

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % ---------------------------------------------------------
\item
  \cventry
  {F. Barlat, \underline{Y. Jeong}, J. Ha, C Tom\'{e}, Myoung-Gyu Lee, W. Wen}
  {\href{https://dx.doi.org/10.4028/www.scientific.net/KEM.725.3}{Advances in Constitutive Modeling of Plasticity for Forming Applications}}
  {Key Engineering Materials}
  {Vol. 725, p3-14, 2017}
  {
  }

>>>>

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % ---------------------------------------------------------
\item
  \cventry
  {\underline{Y. Jeong}, T. Manninen}
  {\href{https://doi.org/10.1088/1742-6596/1063/1/012020}{Formability predictions and measurement of 316L stainless steel using self-consistent crystal plasticity}}
  {Journal of Physics: Conference Series}
  {Vol. 1063, 2018}
  {
  }

  \cventry
  {\underline{Y. Jeong}, S. Panich}
  {\href{https://doi.org/10.1016/j.promfg.2018.07.209}{Forming limits of dual phase steels using crystal plasticity in conjunction with MK approach}}
  {Procedia Manufacturing}
  {Vol. 15, 1816-1824, 2018}
  {
  }

  \cventry
  {D. Steglich \underline{Y. Jeong}}
  {\href{https://doi.org/10.1063/1.5007958}{Texture-based formability prediction for Mg wrought alloys ZE10 and AZ31}}
  {AIP Conference Proceedings}
  {Vol. 1896, 020001, 2017}
  {
  }

  \cventry
  {F. Barlat, \underline{Y. Jeong}, J. Ha, C Tom\'{e}, Myoung-Gyu Lee, W. Wen}
  {\href{https://dx.doi.org/10.4028/www.scientific.net/KEM.725.3}{Advances in Constitutive Modeling of Plasticity for Forming Applications}}
  {Key Engineering Materials}
  {Vol. 725, p3-14, 2017}
  {
  }
